Lessons Learned from the Fast Forward Storage and I/O Project

### 2016-07-18 paper_submitted.tex
added reviews and "plagarism" concerns (fixed via refs). Need to edit a bit more still.

\author{
%\IEEEauthorblockN{Blinded for review},\IEEEauthorblockA{}
\IEEEauthorblockN{Jay Lofstead\IEEEauthorrefmark{1}, Ivo Jimenez\IEEEauthorrefmark{2}, Carlos Maltzahn\IEEEauthorrefmark{2}, Quincey Koziol\IEEEauthorrefmark{3}, John Bent\IEEEauthorrefmark{4}, Eric Barton\IEEEauthorrefmark{5}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Sandia National Laboratories gflofst@sandia.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{2}University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Lawrence Berkeley National Laboratory koziol@lbl.gov}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Segate Government Solutions John.Bent@seagategov.com}
\IEEEauthorblockA{\IEEEauthorrefmark{5}Intel eric.barton@intel.com}
}
\maketitle

@@

Along with analysis of the published design documents, a discussion of the
design philosophy representing the overall intent is presented. This
information represents information that may or may not have been written down,
but is the intent of ultimate system.  This information was gathered through
interviews with the core FFSIO team members. These ideas are presented to give
a fuller picture of where the project is going rather than dwelling on any
limitations of the published documents. This is most important to illustrate
how different concepts will work across layers since that information is spread
across multiple documents and may lack a cohesive overall view. Previously,
a poster~\cite{lofstead:2014:ffsio-poster} and a more detailed evaluation of
consistency and fault tolerance~\cite{lofstead:2014:ffsio-consistency} have
been presented.

@@

The main alternative from scratch design for a file system is
Sirocco~\cite{sirocco,curry:2016:sirocco}. Rather than continuing the striped
design of existing parallel file systems, Sirocco is inspired by peer-to-peer
and object-based systems and includes features like transactions to protect
data modification process independence when writing to avoid coordination
overhead.  The base assumptions are that storage is pervasive and volatile.
Storage devices and locations may come and go randomly, reminiscent of the
Google or Ceph assumptions of regularly failing hardware. When data is pushed
into the system, initial resilience characteristics are guaranteed prior to
returning control back to the user. Then, as system pressures dictate, data
will either replicate as demanded by use and/or migrated towards long-term
resilience requirements.  Unlike the FFSIO project, Sirocco assumes it is
possible that data may be successfully stored in the system, but it is
currently inaccessible because all copies are currently offline. There is also
some potential difficulty in finding data since it will migrate around the
system. To be fair, Sirocco intends to function as the storage layer for a
higher level file system API making many of the awkward system features
invisible to the end user. Sirocco is in the process of being released
publicly.

@@

%\includegraphics[scale=0.07]{logos/doe_logo}
%\includegraphics[scale=0.30]{logos/snl_logo}
%\includegraphics[scale=0.35]{logos/nnsa_logo}
Sandia National Laboratories is a multi-program laboratory managed and operated
by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
Corporation, for the U.S. Department of Energy's National Nuclear Security
Administration under contract DE-AC04-94AL85000.

>>>>

\author{
\IEEEauthorblockN{Blinded for review},\IEEEauthorblockA{}
%\IEEEauthorblockN{Jay Lofstead\IEEEauthorrefmark{1}, Ivo Jimenez\IEEEauthorrefmark{2}, Carlos Maltzahn\IEEEauthorrefmark{2}, Quincey Koziol\IEEEauthorrefmark{3}, John Bent\IEEEauthorrefmark{4}, Eric Barton\IEEEauthorrefmark{5}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}Sandia National Laboratories gflofst@sandia.gov}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}University of California, Santa Cruz ivo@cs.ucsc.edu, carlosm@soe.ucsc.edu}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}HDF Group koziol@hdfgroup.org}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}EMC john.bent@emc.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{5}Intel eric.barton@intel.com}
}
\maketitle

@@

Along with analysis of the published design documents, a discussion of the
design philosophy representing the overall intent is presented. This
information represents information that may or may not have been written down,
but is the intent of ultimate system.  This information was gathered through
interviews with the core FFSIO team members. These ideas are presented to give
a fuller picture of where the project is going rather than dwelling on any
limitations of the published documents. This is most important to illustrate
how different concepts will work across layers since that information is spread
across multiple documents and may lack a cohesive overall view.

@@

The main alternative from scratch design for a file system is
Sirocco~\cite{sirocco}. Rather than continuing the striped design of existing
parallel file systems, Sirocco is inspired by peer-to-peer and object-based
systems and includes features like transactions to protect data modification
process independence when writing to avoid coordination overhead.  The base
assumptions are that storage is pervasive and volatile. Storage devices and
locations may come and go randomly, reminiscent of the Google or Ceph
assumptions of regularly failing hardware. When data is pushed into the system,
initial resilience characteristics are guaranteed prior to returning control
back to the user. Then, as system pressures dictate, data will either replicate
as demanded by use and/or migrated towards long-term resilience requirements.
Unlike the FFSIO project, Sirocco assumes it is possible that data may be
successfully stored in the system, but it is currently inaccessible because all
copies are currently offline. There is also some potential difficulty in
finding data since it will migrate around the system. To be fair, Sirocco
intends to function as the storage layer for a higher level file system API
making many of the awkward system features invisible to the end user. Sirocco
is in the process of being released publicly.

@@

blinded for review

%\includegraphics[scale=0.07]{logos/doe_logo}
%\includegraphics[scale=0.30]{logos/snl_logo}
%\includegraphics[scale=0.35]{logos/nnsa_logo}
%Sandia National Laboratories is a multi-program laboratory managed and operated
%by Sandia Corporation, a wholly owned subsidiary of Lockheed Martin
%Corporation, for the U.S. Department of Energy's National Nuclear Security
%Administration under contract DE-AC04-94AL85000.
